Usable Security in Virtual Power Plants

### 2018-01-22 acmart-master/draft.tex
Made Changes

\section{Related Work}
Usability of security is an area of research that has been largely ignored. More focus has been placed on security itself, hence the presence of extensive literature on security in information systems and lack thereof in the case of usability. Smart grid is a vast interconnection of several different kinds of components across several domains. There are several key components that interact with each other that expose several vulnerabilities\cite{liu2012cyber}. There are several vulnerabilities across communication protocols, legacy devices and technologies. Additionally, when designing a system, new vulnerabilities may be found, rendering current security infrastructure weaker. A cyber-physical approach\cite{mo2012cyber} has been presented to tackle new security challenges. They propose a system model that uses security requirements and vulnerabilities to identify countermeasures. In order to identify security requirements, a concrete network architecture is required. From the architecture, security objectives can be derived and threats can be evaluated to determine the requirements for security. Wang et. al\cite{wang2013cyber} provide a comprehensive categorization and evaluation of network threats and discuss their countermeasures in detail.
\newline 
There is a lack of usability standards that determine the goals of usability for energy systems. Usability is not directly engineered, but is rather a consequence of system engineering. There are guidelines that aid engineers in developing usable systems\cite{nurse2011guidelines}. Standards such as ISO 9241-11\cite{bevan2015iso} state that usability must be measured in terms of effectiveness, efficiency and satisfaction. These terms must be related to the system of interest using performance metrics of the respective system.A first look at such a relation is provided\cite{kainda2010security}, however is not comprehensive enough to establish a concrete relation between systems. In this paper, we build on this idea to derive a usable security by design approach that begins at the design phase\cite{nielsen1992usability}.

@@

Traditional authentication mechanisms are largely based on password based systems. Having a long random password is good advice. It provides a measure of security for guarding access to important information, such as your online banking account. 
Unfortunately, when faced with having to remember several random fifteen character passwords (characters being A to Z, a to z, 0 to 9 and an assortment of other printable characters such as ! @ \# \$ and \%), most users apply a judgement to the value of the information protected by the password and act accordingly. 
Some accounts may have a relatively weak password, because of the cost of undue information leakage or harm to the owner if the account is compromised. Other accounts might have a stronger password because users don't want their money siphoned off by a cyber-criminal. These are judgements about the perceived value of the information. \\
Passwords are also exceptionally susceptible to dictionary and brute force attacks. Simple passwords can be cracked in seconds and longer passwords that include common words and phrases from literature take up to a week to be cracked. Passwords can be called secure if the time required to crack is sufficiently long, such as in years or decades. Such passwords may be constructed from a combination of alphabets, numbers and symbols. There is a trade off though, as such passwords are harder to remember and also hard to enter into a system without errors. It is also compounded by the fact that users are recommended to change passwords periodically. Users tend to create variations of their previous passwords to prevent having to generate a new password and consider using a variant of a previous password easier since they are already familiar with it. This especially problematic since users may forget the password has been changed and do not remember the new password. This invites a lot of pressure onto users who are not technologically friendly and are oblivious to the system structure. Therefore, the most secure passwords and password systems are, in fact, the least usable.

>>>>

\section{Related Work}
Usability of security is an area of research that has been largely ignored. More focus has been placed on security itself, hence the presence of extensive literature on security in information systems and lack thereof in the case of usability. Smart grid is a vast interconnection of several different kinds of components across several domains. There are several key components that interact with each other that expose several vulnerabilities\cite{liu2012cyber}. There are several vulnerabilities across communication protocols, legacy devices and technologies. Additionally, when designing a system, new vulnerabilities may be found, rendering current security infrastructure weaker. A cyber-physical approach\cite{mo2012cyber} has been presented to tackle new security challenges. They propose a system model using security requirements and vulnerabilities to identify countermeasures. In order to identify security requirements, a concrete network architecture is required. From the architecture, security objectives can be derived and threats can be evaluated to determine the requirements for security. Wang et. al\cite{wang2013cyber} provide a comprehensive categorization and evaluation of network threats and discuss their countermeasures in detail.
\newline 
There is a lack of usability standards that determine the goals of usability for energy systems. Usability is not directly engineered, but is rather a consequence of system engineering. There are guidelines that aid engineers in developing usable systems\cite{nurse2011guidelines}. Standards such as ISO 9241-11\cite{bevan2015iso} state that usability must be measured in terms of effectiveness, efficiency and satisfaction. These terms must be related to the system of interest using performance metrics of the respective system. A first look at such a relation is provided\cite{kainda2010security}, however is not comprehensive enough to establish a concrete relation between systems. In this paper, we build on this idea to derive a usable security by design approach that begins at the design phase\cite{nielsen1992usability}.

@@

Traditional authentication mechanisms are largely based on password based systems. Having a long random password is good advice. It provides a measure of security for guarding access to important information, such as your online banking account. 
Unfortunately, when faced with having to remember several random fifteen character passwords (characters being A to Z, a to z, 0 to 9 and an assortment of other printable characters such as ! @ \# \$ and \%), most users apply a judgement to the value of the information protected by the password and act accordingly. 
Some accounts may have a relatively weak password, because of the cost of undue information leakage or harm to the owner if the account is compromised. Other accounts might have a stronger password because users don't want their money siphoned off by a cyber-criminal. These are judgements about the perceived value of the information. \\
Passwords are also exceptionally susceptible to dictionary and brute force attacks. Simple passwords can be cracked in seconds and longer passwords that include common words and phrases from literature take up to a week to be cracked. Passwords can be called secure if the time required to crack is sufficiently long, such as in years or decades. Such passwords may be constructed from a combination of alphabets, numbers and symbols. There is a trade off though, as such passwords are harder to remember and also hard to enter into a system without errors. It is also compounded by the fact that users are recommended to change passwords periodically. Users tend to create variations of their previous passwords to prevent having to generate a new password and consider using a variant of a previous password easier since they are already familiar with it. This is especially problematic since users may forget the password has been changed and do not remember the new password, inviting a lot of pressure onto users who are not technologically friendly and are oblivious to the system structure. Therefore, the most secure passwords and password systems are, in fact, the least usable.
